---
title: "First Exploration"
output: 
  html_document:
    theme: paper
date: "`r Sys.Date()`"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r message=FALSE, warning=FALSE}
pacman::p_load(modelsummary, pwr, survey, broom, dplyr, tidyr, knitr, kableExtra, gt,
               rstatix, ggeffects, ggplot2, gridExtra, magrittr)
```

<br>

# Open data

```{r}
#load("/Users/franciscacastro/Dropbox/Shared_ERC_Francisca_and_Jenny/r-project/environment.Rdata")
load("C:/Users/Francisca/Dropbox/Shared_ERC_Francisca_and_Jenny/r-project/environment.Rdata")
```

<br>

# Data exploration

Mean demographic values by treatment assignment of the following
variables:

-   `race`: 1 = white

-   `gender4`: 1 = male

-   `BGU_knowledge1` to `BGU_knowledge6` for political knowledge

-   `BGU_Trumpapproval`: from 1 = strongly approve to 5 = strongly
    disapprove

-   `CC21_330a` ideology from 1 = very liberal to 7 = very conservative

-   `pid3` party identification with the following categories: 1 =
    democrat 2 = republican 3 = independent

-   `faminc_new`

-   `educ`

```{r}
summary_stats <- data_raw %>%
  group_by(BGU_group) %>%
  summarize(
    mean_race_white = round(mean(race == 1, na.rm = TRUE), 2),
    mean_gender_male = round(mean(gender4 == 1, na.rm = TRUE), 2),
    mean_trump_approve = round(mean(BGU_Trumpapproval %in% c(1, 2), na.rm = TRUE), 2), # strongly and somewhat approve
    mean_ideology = round(mean(ifelse(CC21_330a %in% 1:7, CC21_330a, NA), na.rm = TRUE), 2), # excluding 8 Not sure
    mean_party_dem = round(mean(pid3 == 1, na.rm = TRUE), 2), #democrat
    mean_party_rep = round(mean(pid3 == 2, na.rm = TRUE), 2), #republican
    mean_faminc = round(mean(faminc_new, na.rm = TRUE), 2),
    mean_educ = round(mean(educ, na.rm = TRUE), 2))

# Transform to wide format to make the table

summary_stats_wide <- summary_stats %>%
  pivot_longer(cols = -BGU_group,
               names_to = "metric",
               values_to = "value") %>%
  pivot_wider(names_from = BGU_group,
              values_from = value) %>%
  mutate(metric = c("White", "Male", "Trump Approval", "Ideology", "Democrat", 
                    "Republican", "Income", "Education")) %>%
  rename("Variable" = 1,
         "Control" = 2,
         "Trump Liberal" = 3,
         "Trump Conservative" = 4,
         "Close Friend Liberal" = 5,
         "Close Friend Conservative" = 6)


table <- summary_stats_wide %>%
  kable("html", booktabs = TRUE) %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  column_spec(1:ncol(summary_stats_wide), width = "4cm")

table_latex <- summary_stats_wide %>%
  kable("latex", booktabs = TRUE) %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  column_spec(1:ncol(summary_stats_wide), width = "3cm")

table
```

<br>

# Preliminary analyses

## With long database

Assessing the effect of the treatment on policy positions.

```{r}
models_initial <- list(
  "Initial Model" = lm(policy_opinion ~ libtrump + contrump + libfriend + confriend, data = data_long))


msummary(models_initial,
         stars = c('*' = .1, '**' = .05, '***' = .01))
```

## With wide database

Assesing the effect of the treatment on policy positions *for each
topic*.

```{r}
models_initial_w <- list(
  "Wages" = lm(minimum_wage ~ BGU_group, data = data_wide),
  "Taxes" = lm(taxes ~ BGU_group, data = data_wide),
  "Abortion" = lm(abortion ~ BGU_group, data = data_wide),
  "Immigration" = lm(immigration ~ BGU_group, data = data_wide),
  "Guns" = lm(guns ~ BGU_group, data = data_wide),
  "Health Care" = lm(health ~ BGU_group, data = data_wide),
  "Background Checks" = lm(b_checks ~ BGU_group, data = data_wide),
  "Climate Change" = lm(climate ~ BGU_group, data = data_wide),
  "Planned Parenthood" = lm(p_parent ~ BGU_group, data = data_wide))


msummary(models_initial_w,
         stars = c('*' = .1, '**' = .05, '***' = .01),
         output = 'markdown')

```

Filtered results for the paper

```{r}
models_filtered <- list(
  "Immigration" = lm(immigration ~ BGU_group, data = data_wide),
  "Background \n Checks" = lm(b_checks ~ BGU_group, data = data_wide))


msummary(models_filtered,
         stars = c('*' = .1, '**' = .05, '***' = .01),
         output = "latex")
```

# Interactions

Interactions between:

-   Treatment (close friend) and political knowledge $\rightarrow$
    `knowledge_index`

-   Treatment (close friend) and ideology $\rightarrow$ `ideology` and
    `party_id`

-   Treatment (close friend) and social conformism (when they value
    conformity over autonomy in how they think and behave) $\rightarrow$
    `SCI`

## Political knowledge

```{r}
pol_knowledge_interaction <- list(
  "Wages" = lm(minimum_wage ~ BGU_group * knowledge_index, data = data_wide),
  "Taxes" = lm(taxes ~ BGU_group * knowledge_index, data = data_wide),
  "Abortion" = lm(abortion ~ BGU_group * knowledge_index, data = data_wide),
  "Immigration" = lm(immigration ~ BGU_group * knowledge_index, data = data_wide),
  "Guns" = lm(guns ~ BGU_group * knowledge_index, data = data_wide),
  "Health Care" = lm(health ~ BGU_group * knowledge_index, data = data_wide),
  "Background Checks" = lm(b_checks ~ BGU_group * knowledge_index, data = data_wide),
  "Climate Change" = lm(climate ~ BGU_group * knowledge_index, data = data_wide),
  "Planned Parenthood" = lm(p_parent ~ BGU_group * knowledge_index, data = data_wide)
)

msummary(pol_knowledge_interaction,
         stars = c('*' = .1, '**' = .05, '***' = .01),
         output = 'markdown')
```

### Relevant interactions: Background checks-Trump cue

```{r message=FALSE, warning=FALSE}
model_bchecks <- lm(b_checks ~ BGU_group * knowledge_index, data = data_wide)
effects_TL_bchecks <- ggpredict(model_bchecks, terms = c("knowledge_index", "BGU_group[TL]"))
effects_TC_bchecks <- ggpredict(model_bchecks, terms = c("knowledge_index", "BGU_group[TC]"))

effects_bchecks <- rbind(transform(effects_TL_bchecks, treatment = "TL"),
                       transform(effects_TC_bchecks, treatment = "TC"))

effects_bchecks$treatment <- factor(effects_bchecks$treatment, 
                                  levels = c("TC", "TL"), 
                                  labels = c("Conservative", "Liberal"))

bchecks_plot <- ggplot(effects_bchecks, aes(x = x, y = predicted, color = treatment)) +
  geom_line(aes(group = treatment), size = 1, show.legend = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = treatment), 
              alpha = 0.2, show.legend = FALSE) +
  labs(y = "Background Checks Position", x = "Political Knowledge") +
  theme_minimal() +
  theme(#axis.title.x = element_blank(),     
        axis.title.y = element_text(size = 14))      

bchecks_plot
```


### Relevant interactions: Climate change-Close friend cue
```{r message=FALSE, warning=FALSE}
model_climate <- lm(climate ~ BGU_group * knowledge_index, data = data_wide)
effects_CFL_climate <- ggpredict(model_climate, terms = c("knowledge_index", "BGU_group[CFL]"))
effects_CFC_climate <- ggpredict(model_climate, terms = c("knowledge_index", "BGU_group[CFC]"))

effects_climate <- rbind(transform(effects_CFL_climate, treatment = "CFL"),
                         transform(effects_CFC_climate, treatment = "CFC"))

effects_climate$treatment <- factor(effects_climate$treatment, 
                                  levels = c("CFC", "CFL"), 
                                  labels = c("CF Conservative", "CF Liberal"))

climate_plot <- ggplot(effects_climate, aes(x = x, y = predicted, color = treatment)) +
  geom_line(aes(group = treatment), size = 1, show.legend = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = treatment), 
              alpha = 0.2, show.legend = TRUE) +
  labs(y = "Climate Change Position", x = "Political Knowledge") +
  theme_minimal() +
  theme(#axis.title.x = element_blank(),     
        axis.title.y = element_text(size = 14))     

climate_plot
```

## Ideology

```{r}
ideology_interaction <- list(
  "Wages" = lm(minimum_wage ~ BGU_group * ideology, data = data_wide),
  "Taxes" = lm(taxes ~ BGU_group * ideology, data = data_wide),
  "Abortion" = lm(abortion ~ BGU_group * ideology, data = data_wide),
  "Immigration" = lm(immigration ~ BGU_group * ideology, data = data_wide),
  "Guns" = lm(guns ~ BGU_group * ideology, data = data_wide),
  "Health Care" = lm(health ~ BGU_group * ideology, data = data_wide),
  "Background Checks" = lm(b_checks ~ BGU_group * ideology, data = data_wide),
  "Climate Change" = lm(climate ~ BGU_group * ideology, data = data_wide),
  "Planned Parenthood" = lm(p_parent ~ BGU_group * ideology, data = data_wide))

msummary(ideology_interaction,
         stars = c('*' = .1, '**' = .05, '***' = .01),
         output = 'markdown')
```

## Party identification

```{r}
party_id_interaction <- list(
  "Wages" = lm(minimum_wage ~ BGU_group * party_id, data = data_wide),
  "Taxes" = lm(taxes ~ BGU_group * party_id, data = data_wide),
  "Abortion" = lm(abortion ~ BGU_group * party_id, data = data_wide),
  "Immigration" = lm(immigration ~ BGU_group * party_id, data = data_wide),
  "Guns" = lm(guns ~ BGU_group * party_id, data = data_wide),
  "Health Care" = lm(health ~ BGU_group * party_id, data = data_wide),
  "Background Checks" = lm(b_checks ~ BGU_group * party_id, data = data_wide),
  "Climate Change" = lm(climate ~ BGU_group * party_id, data = data_wide),
  "Planned Parenthood" = lm(p_parent ~ BGU_group * party_id, data = data_wide))

party_id_interaction1 <- list(
  "Wages" = lm(minimum_wage ~ BGU_group * party_id, data = data_wide))

msummary(party_id_interaction1,
         stars = c('*' = .1, '**' = .05, '***' = .01),
         output = 'latex')
```

### Wages and treatments

```{r}
model_wages_pid <- lm(minimum_wage ~ BGU_group * party_id, data = data_wide)
effects_TL_wages_pid <- ggpredict(model_wages_pid, terms = c("party_id", "BGU_group[TL]"))
effects_TC_wages_pid <- ggpredict(model_wages_pid, terms = c("party_id", "BGU_group[TC]"))
effects_CFL_wages_pid <- ggpredict(model_wages_pid, terms = c("party_id", "BGU_group[CFL]"))
effects_CFC_wages_pid <- ggpredict(model_wages_pid, terms = c("party_id", "BGU_group[CFC]"))

effects_wages_pid <- rbind(transform(effects_TL_wages_pid, treatment = "TL"),
                       transform(effects_TC_wages_pid, treatment = "TC"),
                       transform(effects_CFL_wages_pid, treatment = "CFL"),
                       transform(effects_CFC_wages_pid, treatment = "CFC"))

effects_wages_pid$treatment <- factor(effects_wages_pid$treatment, 
                                  levels = c("TL", "TC", "CFL", "CFC"), 
                                  labels = c("Trump Liberal", "Trump Conservative",
                                  "Close Friend Liberal", "Close Friend Conservative"))

wages_pid_plot <- ggplot(effects_wages_pid, aes(x = x, y = predicted)) +
  geom_point(aes(color = group), size = 3, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = group),
                width = 0.2, position = position_dodge(width = 0.5)) +
  labs(y = "Minimum Wages Policy Position", color = "Treatment") +  
  scale_x_discrete(labels=c("democrat" = "Democrat", 
                            "independent/other" = "Independent/Other", 
                            "republican" = "Republican")) + 
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        legend.position = "bottom") +
  scale_y_continuous(limits = c(-0.5, NA))  +
  scale_color_manual(values = c("TL" = "#4C4C4C", "CFL" = "#A0A0A0", 
                                "TC" = "#787878", "CFC" = "#D0D0D0")) 


wages_pid_plot
```
I really like this plot and I think is a candidate to put in the paper. Although it's a little bit weird that the CF Liberal prompt makes people more conservative.

Have in mind that the phrasing of the question is the following: To increase the minimum wage to over 10 USD an hour. A close friend of yours has expressed support for this policy. How about you? Do you support or oppose increasing the minimum wage to over 10 USD an hour?


```{r}
ggsave("wages_party_id.png", wages_pid_plot, width = 4, height = 4, dpi = 300)
```


### Taxes and treatments

```{r}
model_taxes <- lm(taxes ~ BGU_group * party_id, data = data_wide)
effects_TL_taxes <- ggpredict(model_taxes, terms = c("party_id", "BGU_group[TL]"))
effects_TC_taxes <- ggpredict(model_taxes, terms = c("party_id", "BGU_group[TC]"))
effects_CFL_taxes <- ggpredict(model_taxes, terms = c("party_id", "BGU_group[CFL]"))
effects_CFC_taxes <- ggpredict(model_taxes, terms = c("party_id", "BGU_group[CFC]"))

effects_taxes <- rbind(transform(effects_TL_taxes, treatment = "TL"),
                       transform(effects_TC_taxes, treatment = "TC"),
                       transform(effects_CFL_taxes, treatment = "CFL"),
                       transform(effects_CFC_taxes, treatment = "CFC"))

effects_taxes$treatment <- factor(effects_taxes$treatment, 
                                  levels = c("TL", "TC", "CFL", "CFC"), 
                                  labels = c("Trump Liberal", "Trump Conservative",
                                  "Close Friend Liberal", "Close Friend Conservative"))

taxes_plot <- ggplot(effects_taxes, aes(x = x, y = predicted)) +
  geom_point(aes(color = group), size = 3, position = position_dodge(width = 0.5)) + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = group), 
                width = 0.2, position = position_dodge(width = 0.5)) +
  labs(y = "Taxes Policy Position", x = "Party Position") +
  theme_minimal() +
  theme(axis.title.x = element_text(size = 14))


taxes_plot
```

## Social conformism

Interaction between SCI and treatment

```{r}
sci_interaction <- list(
  "Wages" = lm(minimum_wage ~ BGU_group * SCI, data = data_wide),
  "Taxes" = lm(taxes ~ BGU_group * SCI, data = data_wide),
  "Abortion" = lm(abortion ~ BGU_group * SCI, data = data_wide),
  "Immigration" = lm(immigration ~ BGU_group * SCI, data = data_wide),
  "Guns" = lm(guns ~ BGU_group * SCI, data = data_wide),
  "Health Care" = lm(health ~ BGU_group * SCI, data = data_wide),
  "Background Checks" = lm(b_checks ~ BGU_group * SCI, data = data_wide),
  "Climate Change" = lm(climate ~ BGU_group * SCI, data = data_wide),
  "Planned Parenthood" = lm(p_parent ~ BGU_group * SCI, data = data_wide)
)

sci_interaction1 <- list(
  "Guns" = lm(guns ~ BGU_group * SCI, data = data_wide),
  "Health Care" = lm(health ~ BGU_group * SCI, data = data_wide))

msummary(sci_interaction1,
         stars = c('*' = .1, '**' = .05, '***' = .01),
         output = 'latex')
```

The interaction is only significative for the Trump prompt, for selected
models. Therefore, I'll only create interactions for selected models.

For BGU_groupTL × SCI, only wages For BGU_groupTC × SCI, only guns and
healthcare

### Treatment × SCI for wages

```{r}
model_wages <- lm(minimum_wage ~ BGU_group * SCI, data = data_wide)
effects_TL_wages <- ggpredict(model_wages, terms = c("SCI", "BGU_group[TL]"))
effects_TC_wages <- ggpredict(model_wages, terms = c("SCI", "BGU_group[TC]"))

effects_wages <- rbind(transform(effects_TL_wages, treatment = "TL"),
                       transform(effects_TC_wages, treatment = "TC"))

effects_wages$treatment <- factor(effects_wages$treatment, 
                                  levels = c("TC", "TL"), 
                                  labels = c("Conservative", "Liberal"))

wages_plot_sci <- ggplot(effects_wages, aes(x = x, y = predicted, color = treatment)) +
  geom_line(aes(group = treatment), size = 1, show.legend = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = treatment), 
              alpha = 0.2, show.legend = FALSE) +
  labs(y = "Wage Policy Position") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),     
        axis.title.y = element_text(size = 14))     

wages_plot_sci
```

### Guns

```{r}
model_guns <- lm(guns ~ BGU_group * SCI, data = data_wide)
effects_TL_guns <- ggpredict(model_guns, terms = c("SCI", "BGU_group[TL]"))
effects_TC_guns <- ggpredict(model_guns, terms = c("SCI", "BGU_group[TC]"))

effects_guns <- rbind(transform(effects_TL_guns, treatment = "TL"),
                       transform(effects_TC_guns, treatment = "TC"))

effects_guns$treatment <- factor(effects_guns$treatment, 
                                  levels = c("TC", "TL"), 
                                  labels = c("Conservative", "Liberal"))

guns_plot_sci <- ggplot(effects_guns, aes(x = x, y = predicted, color = treatment)) +
  geom_line(aes(group = treatment), size = 1, show.legend = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = treatment), 
              alpha = 0.2, show.legend = FALSE) +
  labs(y = "Guns Policy Position") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_text(size = 14)) +
  scale_color_manual(values = c("Conservative" = "black", "Liberal" = "#A0A0A0")) +
  scale_fill_manual(values = c("Conservative" = "black", "Liberal" = "#A0A0A0"))
           


guns_plot_sci
```
This plot is also interesting, but note that -1 indicates the opposition to allowing teaching to carry guns, and 1 represents the support for it. So, in this case, people with lower levels of social conformisms are more in opposition to the policy, and people with higher levels of social conformism, more in favor of allowing teachers to carry guns. 

### Healthcare

```{r}
model_health <- lm(health ~ BGU_group * SCI, data = data_wide)
effects_TL_health <- ggpredict(model_health, terms = c("SCI", "BGU_group[TL]"))
effects_TC_health <- ggpredict(model_health, terms = c("SCI", "BGU_group[TC]"))

effects_health <- rbind(transform(effects_TL_health, treatment = "TL"),
                       transform(effects_TC_health, treatment = "TC"))

effects_health$treatment <- factor(effects_health$treatment, 
                                  levels = c("TC", "TL"), 
                                  labels = c("Conservative", "Liberal"))

health_plot_sci <- ggplot(effects_health, aes(x = x, y = predicted, color = treatment)) +
  geom_line(aes(group = treatment), size = 1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = treatment), alpha = 0.2) +
  labs(x = "Social Conformism Index (SCI)",
       y = "Health Care Policy Position",
       color = "Treatment",
       fill = "Treatment") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.title.x = element_text(size = 14),       
        axis.title.y = element_text(size = 14),     
        legend.text = element_text(size = 12)) +
  scale_color_manual(values = c("Conservative" = "black", "Liberal" = "#A0A0A0")) +
  scale_fill_manual(values = c("Conservative" = "black", "Liberal" = "#A0A0A0"))
       
 

health_plot_sci
```

<!-- I also like this one --> 

Join the plots

```{r}
interaction_SCI <- grid.arrange(guns_plot_sci, health_plot_sci, ncol = 1, heights = c(1, 1.2)) 

ggsave("interaction_SCI.png", interaction_SCI, width = 6, height = 8, dpi = 600)
```
