---
title: "Publication Outputs"
output: 
  html_document:
    theme: paper
date: "`r Sys.Date()`"
editor_options: 
  markdown: 
    wrap: 72
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r message=FALSE, warning=FALSE}
pacman::p_load(modelsummary, pwr, survey, broom, dplyr, tidyr, knitr, kableExtra, gt,
               rstatix, ggeffects, ggplot2, gridExtra, magrittr, xtable, psych)
```

# Open data

```{r}
#load("/Users/franciscacastro/Dropbox/Shared_ERC_Francisca_and_Jenny/r-project/environment.Rdata") mac
load("C:/Users/Francisca/Dropbox/Shared_ERC_Francisca_and_Jenny/r-project/environment.Rdata") #windows
```

# Figures

## Figure 1 - Average treatment effect of policy cues 

Replication of Figure 1 ATE Across Issues on Barber & Pope (2019) but without separating by party

```{r}
model1 <- lm(policy_opinion ~ male + pid3 + treatment_group, data = data_long)

ate_m1 <- tidy(model1) %>%
  filter(term %in% c("treatment_groupTL", "treatment_groupTC", "treatment_groupCFL", "treatment_groupCFC")) %>%
  mutate(term = case_when(
    term == "treatment_groupTL" ~ "Liberal Trump",
    term == "treatment_groupTC" ~ "Conservative Trump",
    term == "treatment_groupCFL" ~ "Liberal Close Friend",
    term == "treatment_groupCFC" ~ "Conservative Close Friend",
    TRUE ~ term))

ate_m1$term <- factor(ate_m1$term, levels = c(
  "Liberal Trump", 
  "Conservative Trump", 
  "Liberal Close Friend", 
  "Conservative Close Friend"))


# Calculate CI
ate_m1 <- ate_m1 %>%
  mutate(
    conf.low = estimate - 1.96 * std.error,
    conf.high = estimate + 1.96 * std.error
  )


# Plot
ate_plot <- ggplot(ate_m1, aes(x = term, y = estimate)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.05) +
  geom_point(position = position_dodge(width = 0.7), size = 3) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  xlab("Treatment Conditions") +
  ylab("Average Treatment Effect") +
  scale_x_discrete(labels = c("Liberal\nTrump", 
                              "Conservative\nTrump", 
                              "Liberal\nClose Friend", 
                              "Conservative\nClose Friend")) +
  scale_y_continuous(limits = c(-0.25, 0.25)) +
  theme_minimal() +
  theme(legend.position = "none",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())

ate_plot

ggsave("C:/Users/Francisca/Dropbox/Shared_ERC_Francisca_and_Jenny/r-project/output/figures/ate_polsupport.png", 
       ate_plot, width = 5, height = 4, dpi = 600)
```

## Figure 2 - Interaction with Party ID 

```{r}
model2 <- lm(policy_opinion ~ male + party_id + treatment_group*party_id, data = data_long)

m2_TL <- ggpredict(model2, terms = c("party_id", "treatment_group[TL]"))
m2_TC <- ggpredict(model2, terms = c("party_id", "treatment_group[TC]"))
m2_CFL <- ggpredict(model2, terms = c("party_id", "treatment_group[CFL]"))
mw_CFC <- ggpredict(model2, terms = c("party_id", "treatment_group[CFC]"))

model2_table <- rbind(transform(m2_TL, treatment = "TL"),
                      transform(m2_TC, treatment = "TC"),
                      transform(m2_CFL, treatment = "CFL"),
                      transform(mw_CFC, treatment = "CFC"))

model2_table$treatment <- factor(model2_table$treatment,
                                 levels = c("TL", "TC", "CFL", "CFC"),
                                 labels = c("Liberal Trump", "Conservative Trump",
                                            "Liberal Close Friend", "Conservative Close Friend"))

model2_plot <- ggplot(model2_table, aes(x = treatment, y = predicted, group = x)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = x),
                width = 0.2, position = position_dodge(width = 0.25)) +
  geom_point(aes(color = x), size = 3, position = position_dodge(width = 0.25)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  labs(y = "ATE Policy Support", color = "Party Identification") + 
  theme_minimal() +
  theme(axis.title.x = element_blank(), legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.position = "bottom", panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  scale_y_continuous(breaks = seq(-0.3, 0.6, by = 0.30), limits = c(-0.3, 0.6)) +
  scale_x_discrete(labels = c("Liberal\nTrump", 
                              "Conservative\nTrump", 
                              "Liberal\nClose Friend", 
                              "Conservative\nClose Friend")) +
  scale_color_manual(values = c("Democrat" = "black", 
                                "Independent/Other" = "#787878", 
                                "Republican" = "gray")) 


model2_plot

ggsave("C:/Users/Francisca/Dropbox/Shared_ERC_Francisca_and_Jenny/r-project/output/figures/ate_party_id.png", 
       model2_plot, width = 5, height = 4, dpi = 600)
```


## Figure 3 - Interaction with political knowledge

```{r}
model3 <- lm(policy_opinion ~ male + pid3 + knowledge + treatment_group*knowledge, data = data_long)

m3_TL <- ggpredict(model3, terms = c("knowledge", "treatment_group[TL]"))
m3_TC <- ggpredict(model3, terms = c("knowledge", "treatment_group[TC]"))
m3_CFL <- ggpredict(model3, terms = c("knowledge", "treatment_group[CFL]"))
m3_CFC <- ggpredict(model3, terms = c("knowledge", "treatment_group[CFC]"))

model3_table <- rbind(transform(m3_TL, treatment = "TL"),
                      transform(m3_TC, treatment = "TC"),
                      transform(m3_CFL, treatment = "CFL"),
                      transform(m3_CFC, treatment = "CFC"))

model3_table$treatment <- factor(model3_table$treatment,
                                 levels = c("TL", "TC", "CFL", "CFC"),
                                 labels = c("Liberal Trump", "Conservative Trump",
                                            "Liberal Close Friend", "Conservative Close Friend"))


model3_plot <- ggplot(model3_table, aes(x = x, y = predicted, group = treatment)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                width = 0.15, position = position_dodge(width = 0.25), color = "black") +
  geom_point(size = 3, position = position_dodge(width = 0.25), color = "black") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  facet_wrap(~treatment, scales = "free", ncol = 2) +
  labs(y = "Average Treatment Effect", x = "Level of Political Knowledge") +
  theme_minimal() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_text(size = 10),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        panel.border = element_rect(linetype = "solid", fill = NA, color = "black", size = 0.5)) +
  scale_x_continuous(breaks = 0:6) +
  coord_cartesian(ylim = c(-0.1, 0.6))  # Set y-axis limits with coord_cartesian


model3_plot

ggsave("C:/Users/Francisca/Dropbox/Shared_ERC_Francisca_and_Jenny/r-project/output/figures/ate_pol_knowledge.png", 
       model3_plot, width = 5, height = 4, dpi = 600)
```

## Figure 4 - Interaction with social conformism

```{r}
model_4 <- lm(policy_opinion ~ male + pid3 + treatment_group*SCI, data = data_long)

m4_TL <- ggpredict(model_4, terms = c("SCI", "treatment_group[TL]"))
m4_TC <- ggpredict(model_4, terms = c("SCI", "treatment_group[TC]"))
m4_CFL <- ggpredict(model_4, terms = c("SCI", "treatment_group[CFL]"))
m4_CFC <- ggpredict(model_4, terms = c("SCI", "treatment_group[CFC]"))

model4_table <- rbind(transform(m4_TL, treatment = "TL"),
                      transform(m4_TC, treatment = "TC"),
                      transform(m4_CFL, treatment = "CFL"),
                      transform(m4_CFC, treatment = "CFC"))

model4_table$treatment <- factor(model4_table$treatment, 
                                  levels = c("TL", "TC", "CFL", "CFC"), 
                                  labels = c("Liberal Trump", "Conservative Trump",
                                             "Liberal Close Friend", "Conservative Close Friend"))

# Subset the data for Trump 
m4_trump_effects <- subset(model4_table, treatment %in% c("Liberal Trump", "Conservative Trump"))

# Subset the data for Close Friend 
m4_cf_effects <- subset(model4_table, treatment %in% c("Liberal Close Friend", "Conservative Close Friend"))

# Plot for Trump treatments
m4_plot_trump <- ggplot(m4_trump_effects, aes(x = x, y = predicted, color = treatment)) +
  geom_line(aes(group = treatment), size = 1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = treatment), alpha = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add dashed line at y=0
  labs(y = "Average Treatment Effect", title = "Trump Treatments",
       x = "Social Conformism Index (SCI)",  color = " ", fill = " ") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.grid.major = element_blank(),  # Remove major grid lines
        panel.grid.minor = element_blank(),  # Remove minor grid lines
        panel.background = element_rect(fill = "white", colour = "black"),
        legend.text = element_text(size = 7)) + 
  scale_color_manual(values = c("Liberal Trump" = "black", "Conservative Trump" = "#A0A0A0")) +
  scale_fill_manual(values = c("Liberal Trump" = "black", "Conservative Trump" = "#A0A0A0")) +
  ylim(-0.25, 0.5)

m4_plot_trump


# Plot for Close Friend treatments
m4_plot_cf <- ggplot(m4_cf_effects, aes(x = x, y = predicted, color = treatment)) +
  geom_line(aes(group = treatment), size = 1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = treatment), alpha = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add dashed line at y=0
  labs(y = "Average Treatment Effect", title = "Close Friend Treatments",
       x = "Social Conformism Index (SCI)", color = " ", fill = " ") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.grid.major = element_blank(),  # Remove major grid lines
        panel.grid.minor = element_blank(),  # Remove minor grid lines
        panel.background = element_rect(fill = "white", colour = "black"),
        legend.text = element_text(size = 7)) +  # Add background
  scale_color_manual(values = c("Liberal Close Friend" = "black", "Conservative Close Friend" = "#A0A0A0")) +
  scale_fill_manual(values = c("Liberal Close Friend" = "black", "Conservative Close Friend" = "#A0A0A0")) +
  ylim(-0.25, 0.5)

m4_plot_cf

m4_plot_final <- grid.arrange(m4_plot_trump, m4_plot_cf, nrow = 2) 

ggsave("C:/Users/Francisca/Dropbox/Shared_ERC_Francisca_and_Jenny/r-project/output/figures/ate_sci.png", 
       m4_plot_final, width = 3.5, height = 7, dpi = 600)
```


# Supplementary Information

## Table B1.1 - Mean Demographic Values by Treatment Group

```{r}
data_balance <- data_long[data_long$policy_position == "1",]
table(data_balance$treatment_group)

by(data_balance$age, data_balance$treatment_group, mean)
summary(model1 <- lm(age ~ libtrump + contrump + libfriend + confriend, data = data_balance))

by(data_balance$race_white, data_balance$treatment_group, mean)
summary(model1 <- lm(race_white ~  libtrump + contrump + libfriend + confriend, data = data_balance))

by(data_balance$male, data_balance$treatment_group, mean)
summary(model1 <- lm(male ~  libtrump + contrump + libfriend + confriend, data = data_balance)) # significant

by(data_balance$knowledge, data_balance$treatment_group, mean)
summary(model1 <- lm(knowledge ~  libtrump + contrump + libfriend + confriend, data = data_balance))

by(data_balance$trump_approve, data_balance$treatment_group, mean, na.rm = T)
summary(model1 <- lm(trump_approve ~ libtrump + contrump + libfriend + confriend, data = data_balance))

by(data_balance$ideo5, data_balance$treatment_group, function(x) mean(x, na.rm = T))
summary(model1 <- lm(ideo5 ~  libtrump + contrump + libfriend + confriend, data = data_balance))

by(data_balance$pid7, data_balance$treatment_group, function(x) mean(x, na.rm = T))
summary(model1 <- lm(pid7 ~  libtrump + contrump + libfriend + confriend, data = data_balance))

by(data_balance$faminc_new, data_balance$treatment_group, function(x) mean(x, na.rm = T))
summary(model1 <- lm(faminc_new ~  libtrump + contrump + libfriend + confriend, data = data_balance))

by(data_balance$educ, data_balance$treatment_group, function(x) mean(x, na.rm = T))
summary(model1 <- lm(educ ~  libtrump + contrump + libfriend + confriend, data = data_balance))

by(data_balance$newsint, data_balance$treatment_group, function(x) mean(x, na.rm = T))
summary(model1 <- lm(newsint ~  libtrump + contrump + libfriend + confriend, data = data_balance))

by(data_balance$republican, data_balance$treatment_group, function(x) mean(x, na.rm = T))
summary(model1 <- lm(republican ~  libtrump + contrump + libfriend + confriend, data = data_balance))

by(data_balance$democrat, data_balance$treatment_group, function(x) mean(x, na.rm = T))
summary(model1 <- lm(democrat ~  libtrump + contrump + libfriend + confriend, data = data_balance))

by(data_balance$independent, data_balance$treatment_group, function(x) mean(x, na.rm = T))
summary(model1 <- lm(independent ~ libtrump + contrump + libfriend + confriend, data = data_balance)) #party id somewhat significant, we might want to control

descriptive_stats <- data_balance %>%
  group_by(treatment_group) %>%
  summarise(across(c(age, race_white, male, knowledge, trump_approve, ideo5, pid7, 
                     faminc_new, educ, newsint, republican, democrat, independent),
                   list(mean = ~mean(., na.rm = TRUE)), .names = "{.col}_{.fn}")) 

descriptive_stats_long <- descriptive_stats %>%
  pivot_longer(cols = -treatment_group,
               names_to = "metric",
               values_to = "value") %>%
  pivot_wider(names_from = treatment_group,
              values_from = value) %>%
  mutate(metric = c("Age", "White", "Male", "Knowledge", 
                    "Trump Approval", "5-point Ideology", "7-point Ideology", 
                    "Income", "Education", "Political Interest", 
                    "Republican", "Democrat", "Independent")) %>%
  rename("Variable" = metric,
         "Control" = `control`,
         "Liberal Trump" = `TL`,
         "Conservative Trump" = `TC`,
         "Liberal Close Friend" = `CFL`,
         "Conservative Close Friend" = `CFC`) %>%
  mutate(across(-Variable, ~round(., 2)))


latex_table <- kable(descriptive_stats_long, format = "latex", booktabs = TRUE) 
descriptive_stats_long
```

## Table B2.1 - Test for Cronbach's alpha

```{r}
items_sci_full <- data_long %>% 
  select(BGU_conf1_rec, BGU_conf2_rec, BGU_conf3_rec, BGU_conf4_rec, BGU_conf5_rec, BGU_conf6_rec)

ca_sci <- alpha(items_sci_full, check.keys=TRUE)
print(ca_sci)
```

```{r eval=FALSE}
item_stats <- as.data.frame(ca_sci$item.stats)
latex_table_items <- xtable(item_stats)
print(latex_table_items, type = 'latex') 
```

## Table C1.1 Average Treatment Effect of Policy Cue

```{r}
msummary(model1,
         title = "Average Treatment Effect of Policy Cue",
         stars = c('*' = .1, '**' = .05, '***' = .01),
         estimate = "{estimate}{stars} ({std.error})",
         statistic = NULL,
         output = 'markdown')
```

## Table C1.2 - Treatment effect per policy issues

```{r}
models_pol_issues <- list(
  "Wages" = lm(policy_opinion ~ male + pid3 + treatment_group, data = data_long[data_long$policy_issue == 1, ]),
  "Taxes" = lm(policy_opinion ~ male + pid3 + treatment_group, data = data_long[data_long$policy_issue == 2, ]),
  "Abortion" = lm(policy_opinion ~ male + pid3 + treatment_group, data = data_long[data_long$policy_issue == 3, ]),
  "Immigration" = lm(policy_opinion ~ male + pid3 + treatment_group, data = data_long[data_long$policy_issue == 4, ]),
  "Guns" = lm(policy_opinion ~ male + pid3 + treatment_group, data = data_long[data_long$policy_issue == 5, ]),
  "Health Care" = lm(policy_opinion ~ male + pid3 + treatment_group, data = data_long[data_long$policy_issue == 6, ]),
  "Background Checks" = lm(policy_opinion ~ male + pid3 + treatment_group, data = data_long[data_long$policy_issue == 7, ]),
  "Climate Change" = lm(policy_opinion ~ male + pid3 + treatment_group, data = data_long[data_long$policy_issue == 8, ]),
  "Planned Parenthood" = lm(policy_opinion ~ male + pid3 + treatment_group, data = data_long[data_long$policy_issue == 9, ]))

msummary(models_pol_issues,
         stars = c('*' = .1, '**' = .05, '***' = .01),
         output = 'markdown')
```

## Interactions

### Table C3.1 With Party ID

```{r}
msummary(model2,
         title = "Interaction with Party Identification",
         stars = c('*' = .1, '**' = .05, '***' = .01),
         estimate = "{estimate}{stars} ({std.error})",
         statistic = NULL,
         output = 'markdown')
```

### Table C3.2 With Political Knowledge

```{r}
msummary(model3,
         title = "Interaction with Political Knowledge",
         stars = c('*' = .1, '**' = .05, '***' = .01),
         estimate = "{estimate}{stars} ({std.error})",
         statistic = NULL,
         output = 'markdown')
```

### Table C3.3 With Social Conformism

```{r}
msummary(model_4,
         title = "Interaction with Social Conformism Index",
         stars = c('*' = .1, '**' = .05, '***' = .01),
         estimate = "{estimate}{stars} ({std.error})",
         statistic = NULL,
         output = 'markdown')
```


# Figures

## Figure 1 - Distribution political knowledge

```{r}
pol_knowledge_plot <- data_long[data_long$policy_issue == 1, ] %>%
  count(knowledge) %>%
  ggplot(aes(x = knowledge, y = n)) +
  geom_bar(stat = "identity") +
  labs(x = "Number of Correct Answers",
       y = "Number of Observations") +
  scale_x_continuous(breaks = seq(min(data_long$knowledge), max(data_long$knowledge), by = 1)) +
  scale_y_continuous(limits = c(0, 250)) +  
  theme_minimal()

pol_knowledge_plot

ggsave("C:/Users/Francisca/Dropbox/Shared_ERC_Francisca_and_Jenny/r-project/output/figures/pol_knowledge.png", pol_knowledge_plot, width = 8, height = 6, dpi = 600)

```

























